How do changes in ex vary between countries?

### 2022-03-09 draft_paper.Rmd
did simulated annealing; shouldn't have...

>>>>

# Now let's finish with the most unneccesarily complicated variant: using a different algorithm in 
# optim which will allow local minima to be escaped. This is the simulated annealing method 
# (method = "SANN") which is based on physics models. Unfortunately this is not a bounded algoritm,
# i.e. does not take values within limits, so instead the parameter passed to it has to be 
# converted and deconverted from a bounded range using a link function. 
# This can be done with a modification of the sigmoid function, which shifts the transformed 
# value from the range 0-1 to the range lower_tau-upper_tau.

# Let's build up this function as follows:

# sigmoid_shift <- function(x, lower = 0, upper = 1){
#   (upper - lower) / (1 + exp(-x)) + lower
# }
# # 
# curve(sigmoid_shift, -3, 3) # basic sigmoid 
# 
# sigmoid_shift2 <- function(x){
#   sigmoid_shift(x = x, lower = 1981, upper = 2015)
# }
# 
# curve(sigmoid_shift2, -3, 3)

# So this will work as a transformation from an unbounded space (x) to a 
# bounded space (f(x))

# We'll also need to reverse the operation

# # After a bit of pen-and-paper algebra...
# sigmoid_unshift <- function(z, lower = 0, upper = 1){
#   -log((upper - lower) / (z - lower) -1)
# }
# 
# Let's double check...

#  
# sigmoid_shift(-4, lower = 1982, upper = 2015) %>% 
#   sigmoid_unshift(lower = 1982, upper = 2015)
# 
# 
# 
# get_best_tau_from_optim_sann <- function(df, buffer = 2, what = c("tau", "tau_z", "optim")){
#   # We can put in some data validation checks too 
#   sigmoid_shift <- function(x, lower = 0, upper = 1){
#     (upper - lower) / (1 + exp(-x)) + lower
#   }
#  
#   sigmoid_unshift <- function(z, lower = 0, upper = 1){
#   -log((upper - lower) / (z - lower) -1)
#   } 
#   
#   
#   what <- match.arg(what)
#   
#   years <- df$year 
#   tau_lower <- min(years) + buffer # the lower bound 
#   tau_upper <- max(years) - buffer # the upper bound
#   # tau_start <- (tau_upper + tau_lower) / 2 # start just in the middle 
#   # (This shouldn't matter if the algorithm is robust) 
#   
#   get_result_from_model <- function(par, df, what = c("AIC", "BIC", "model")){
#     # Again, can carry out more validation checks 
#     what <- match.arg(what)
#     
#     tau_z <- par[["tau_z"]] # This is how parameters are packed up by optim
#     tau   <- sigmoid_shift(tau_z, lower = tau_lower, upper = tau_upper)
#     
#     model <-
#       df %>% 
#         arrange(year) %>% 
#         mutate(delta_ex = ex - lag(ex)) %>% 
#         filter(!is.na(delta_ex)) %>% 
#         mutate(T_param = ifelse(year < tau, FALSE, TRUE)) %>% 
#         lm(delta_ex ~ T_param, data = .)
# 
#     if (what == "model") {return(model)      }
#     if (what == "BIC")   {return(BIC(model)) }
#     if (what == "AIC")   {return(AIC(model)) }
#     
#     # NULL should never be returned! If it has something's gone wrong!
#     NULL
#   }
# 
#   optim_obj <- 
#     optim(
#       par = list(tau_z = 0), 
#       fn = get_result_from_model, 
#       method = "SANN",
#       df = df
#     )
# 
#   # Need to make the result dependent on the what argument
#   
#   if (what == "tau") {return(sigmoid_shift(optim_obj[["par"]], lower = tau_lower, upper = tau_upper))}
#   if (what == "tau_z") {return(optim_obj[["par"]])}  
#   else if (what == "optim"){ return(optim_obj) }
#   
#   # Again, the following should never be triggered
#   NULL
# }
# 
# 
# sann_estimates <- 
#   hmd_ex_selected_countries_with_synth %>%
#     filter(year >= 1979) %>% 
#     group_by(code, x, sex) %>% 
#     nest() %>% 
#     mutate(
#       best_tau = map_dbl(data, get_best_tau_from_optim_sann)
#     )
# 
# # This takes ABSOLUTELY AGES, and really is the sledgehammer-to-crack
# # -a-nut approach to use only as a last resort. #
# # However if you ever do have a complex and non-finite fitness 
# # surface to try to optimise, and it also requires searching 
# # over a bounded area, then this is how you can do it!
